---
title: "Bayesian Network by Gender"
author: "BH"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document: default
always_allow_html: true
---

```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}
library(haven) 
library(tidyverse) 
library(bnlearn) 
library(qgraph) 
library(mice) 
library(bnviewer)
```

#Set working directory and load dataset as BN_data <- read_sav("provide file location")
```{r include=FALSE}

setwd("C:/Users/Brian/Google Drive/UNIVERSITY/PhD/Rfiles/sex_gambling/BN")

BN_data <- read_sav("C:/Users/Brian/Google Drive/UNIVERSITY/PhD/Rfiles/sex_gambling/BN/cs_dataset_937_labelled.sav") 
```

```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}

data <- BN_data %>%
  select(5,111:116,215:225)

non_labelled <- sapply(data, haven::zap_labels) ## removing labels to impute values
Compdata <- as_tibble(complete(mice(non_labelled, m=5, maxit = 50, method = 'pmm', seed = 500),2))

Males <- Compdata %>%
  filter(Gender==1)%>%
  select(!Gender)

Females <- Compdata %>%
  filter(Gender==0)%>%
  select(!Gender)

#cdata1 <- Compdata %>%
#  select(!Gender)
```

#Male Network - Hill climbing algorithm is used to learn/determine the initial structure of the Bayesian network
```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}
BNhcMales <- hc(Males)
BNhcMales
```

#Female Network - Hill climbing algorithm is used to learn/determine the initial structure of the Bayesian network
```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}
BNhcFemales <- hc(Females)
BNhcFemales
```

#Male network is bootstrapped with 5000 iterations to obtain a stable network
#Male network is averaged while retaining edges (arcs) which appear in 85% of the bootstrapped samples
```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}

#BSThcMale <- boot.strength(Males, R = 5000, algorithm = "hc",
#                    debug = TRUE, cpdag = TRUE)

#saveRDS(BSThcMale, file = "BSThcMale.RDS")
BSThcMale <- readRDS("BSThcMale.RDS")

write.csv(BSThcMale, file = "BSThcMale.csv")

avgnetMale85 <- averaged.network(BSThcMale, threshold = 0.85)
avgnetMale85

```
#Plot male network
```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}

bayesianNetwork.boot.strength.Male = BSThcMale
#boot.strength(Males, R = 5000, algorithm = "hc")

avg.bayesianNetwork.Male = averaged.network(bayesianNetwork.boot.strength.Male, threshold = 0.85)

strength.viewer(
	avg.bayesianNetwork.Male,
	bayesianNetwork.boot.strength.Male,
	bayesianNetwork.background = "white",
	bayesianNetwork.arc.strength.threshold.expression = c("@threshold > 0 & @threshold < 0.85",
								"@threshold >= 0.85 & @threshold <= 0.90",
								"@threshold > 0.90 & @threshold <= 1"),

	bayesianNetwork.arc.strength.threshold.expression.color  = c("grey", "light blue", "blue"),
	bayesianNetwork.arc.strength.threshold.alternative.color =  "white",
	
	bayesianNetwork.arc.strength.tooltip = T,
	
	bayesianNetwork.edge.scale.min = .1,
	bayesianNetwork.edge.scale.max = 5,
	
	bayesianNetwork.arc.strength.label = F,
	bayesianNetwork.edge.scale.label.min = 12,
	bayesianNetwork.edge.scale.label.max = 12,
	node.shape = "circle",
	node.size = 24,
	node.colors = list(background = "#97c2fc",
                     border = "#2b7ce9",
                     highlight = list(background = "#e91eba",
                                      border = "#2b7ce9")),
node.label.prefix = "",
  node.font = list(color = "black", face="source sans pro black"),
	
	bayesianNetwork.width = "100%",
	bayesianNetwork.height = "800px",
	bayesianNetwork.layout = "layout_with_sugiyama")

```

#Female network is bootstrapped with 5000 iterations to obtain a stable network
#Female network is averaged while retaining edges (arcs) which appear in 85% of the bootstrapped samples
```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}

#BSThcFemale <- boot.strength(Females, R = 5000, algorithm = "hc",
 #                          debug = TRUE, cpdag = TRUE)

#saveRDS(BSThcFemale, file = "BSThcFemale.RDS")
BSThcFemale <- readRDS("BSThcFemale.RDS")

write.csv(BSThcFemale, file = "BSThcFemale.csv")

avgnetFemale85 <- averaged.network(BSThcFemale, threshold = .85)
avgnetFemale85

```

#Plot female network
```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}

bayesianNetwork.boot.strength.Female = BSThcFemale
  #boot.strength(Females, R = 200, algorithm = "hc")

avg.bayesianNetwork.Female = averaged.network(bayesianNetwork.boot.strength.Female, threshold = 0.85)

strength.viewer(
	avg.bayesianNetwork.Female,
	bayesianNetwork.boot.strength.Female,
	bayesianNetwork.background = "white",
	bayesianNetwork.arc.strength.threshold.expression = c("@threshold > 0 & @threshold < 0.85",
								"@threshold >= 0.85 & @threshold <= 0.9",
								"@threshold > 0.9 & @threshold <= 1"),

	bayesianNetwork.arc.strength.threshold.expression.color  = c("red", "light blue", "blue"),
	bayesianNetwork.arc.strength.threshold.alternative.color =  "white",
	
	bayesianNetwork.arc.strength.tooltip = T,
	
	bayesianNetwork.edge.scale.min = .1,
	bayesianNetwork.edge.scale.max = 5,
	
	bayesianNetwork.arc.strength.label = F,
	bayesianNetwork.edge.scale.label.min = 12,
	bayesianNetwork.edge.scale.label.max = 12,
	node.shape = "circle",
	node.size = 24,
	node.colors = list(background = "#97c2fc",
                     border = "#2b7ce9",
                     highlight = list(background = "#e91eba",
                                      border = "#2b7ce9")),
node.label.prefix = "",
  node.font = list(color = "black", face="source sans pro black"),
	
	bayesianNetwork.width = "100%",
	bayesianNetwork.height = "800px",
	bayesianNetwork.layout = "layout_with_sugiyama")

```


#Output of directed relationships in MALE bootstrapped model including estimates of strength and direction
```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}
BSThcMale
```

#Output of directed relationships in FEMALE bootstrapped model including estimates of strength and direction
```{r echo=TRUE, tidy=TRUE, warning=FALSE, message=FALSE}
BSThcFemale
```

